Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-11-30 article.qmd
Show model repr from BioModels figure
Align equations in figures

::: {#fig-first-order layout-ncol=3}
```{python}
class Decay(System):
    x: Variable = initial(default=1)
    eq = x.derive() << -x

@@

::: {#fig-second-order layout-ncol=3}
```{python}
class Oscillator(System):
    x: Variable = initial(default=1)
    v: Derivative = x.derive(initial=0)
    eq = v.derive() << -x

@@

::: {#fig-composition layout-ncol=3}
```{python}
class BigModel(System):
    x: Variable = initial(default=1)
    linked = Decay(x=x)
    independent = Decay(x=2)

@@

::: {#fig-parameter layout-nrow=2}
![](src/ide/constant.png)

@@

::: {#fig-composition layout-nrow=1}
![](src/ide/composition_tooltip.png)

@@

::: {layout-ncol=2}
```{python}
class Model(Compartment):
    """2A -> B"""

@@

model = sbml.load("repressilator.sbml")  # from existing SBML file
model = biomodels.load_model("BIOMD12")  # from BioModels
```

>>>>

::: {#fig-first-order layout-ncol=3 layout-valign="center"}
```{python}
class Decay(System):
    x: Variable = initial(default=1)
    eq = x.derive() << -x

@@

::: {#fig-second-order layout-ncol=3 layout-valign="center"}
```{python}
class Oscillator(System):
    x: Variable = initial(default=1)
    v: Derivative = x.derive(initial=0)
    eq = v.derive() << -x

@@

::: {#fig-composition layout-ncol=3 layout-valign="center"}
```{python}
class BigModel(System):
    x: Variable = initial(default=1)
    linked = Decay(x=x)
    independent = Decay(x=2)

@@

::: {#fig-parameter layout-nrow=2 layout-valign="bottom"}
![](src/ide/constant.png)

@@

::: {#fig-composition layout-nrow=1 layout-valign="bottom"}
![](src/ide/composition_tooltip.png)

@@

::: {layout-ncol=2 layout-valign="center"}
```{python}
class Model(Compartment):
    """2A -> B"""

@@

model = sbml.load("repressilator.sbml")  # from existing SBML file
model = biomodels.load_model("BIOMD12")  # from BioModels
model
```
